---
title: "Analysis"
format: html
editor:
    render-on-save: true
execute:
  cache: true
editor_options: 
  chunk_output_type: console
---

## Methods

```{r}
#| output: false
library(tidyverse)
library(easystats)
library(rstanarm)
library(bayestestR)
library(insight)
library(see)
library(corrplot)

df <- read.csv("../data/data.csv") |>
  mutate(IAS_TOTAL = (IAS_1 + IAS_2 + IAS_3 + IAS_4 + IAS_5 + IAS_6 + IAS_7 + IAS_8 + IAS_9 + IAS_10 + IAS_11 + IAS_12 + IAS_13 + IAS_14 + IAS_15 + IAS_16 + IAS_17 + IAS_18 + IAS_19 + IAS_20 + IAS_21) / 21)
```

### Participants

```{r}
report_participants(df, age = "Age", gender = "Gender", race = "Ethnicity")
```


```{r}
clean <- df |>
  select(participant_id, IAS_TOTAL, MAIA_Noticing, PI_Alive, PI_Understandable, PI_Hierarchical, HCT_Accuracy, HCT_Awareness, HCT_Sensibility)
```


## Results

### Correlation between Interoceptive Measures

```{r}
r <- clean |> 
  select(-starts_with("PI_"), -participant_id) |> 
  correlation(bayesian = TRUE)

r |> 
  summary(redundant = TRUE) |> 
  cor_sort() |> 
  plot()
```

### Correlation between Primal Beliefs


```{r}
r <- clean |> 
  select(starts_with("PI_")) |> 
  correlation(bayesian = TRUE)

r %>%
  summary(redundant = TRUE) |> 
  cor_sort() |> 
  plot()
```

### Correlation between Interoception and Primals

```{r}
r <- correlation(select(clean, starts_with("PI_")), 
                 select(clean, starts_with("MAIA_"), starts_with("HCT_"), starts_with("IAS")),
                 bayesian = TRUE) |> 
  arrange(desc(BF))
r

r %>%
  summary() |> 
  plot()
```


```{r}
# Plot scatter plot (i.e., detailed pattern) for selected correlations
cor_test(clean, "PI_Alive", "HCT_Sensibility", bayesian=TRUE) |> 
  plot()
```















## Old



### Bayes

#### Posterior for PI-alive and HCT-accuracy

```{r}
modelaa <- stan_glm(PI_Alive ~ HCT_Accuracy, data = clean)

posteriorsaa <- get_parameters(modelaa)

head(posteriorsaa)

ggplot(posteriorsaa, aes(x = HCT_Accuracy)) +
  geom_density(fill = "orange")

mean(posteriorsaa$HCT_Accuracy)

median(posteriorsaa$HCT_Accuracy)

map_estimate(posteriorsaa$HCT_Accuracy)

ggplot(posteriorsaa, aes(x = HCT_Accuracy)) +
  geom_density(fill = "orange") +
  # The mean in blue
  geom_vline(xintercept = mean(posteriorsaa$HCT_Accuracy), color = "blue", linewidth = 1) +
  # The median in red
  geom_vline(xintercept = median(posteriorsaa$HCT_Accuracy), color = "red", linewidth = 1) +
  # The MAP in purple
  geom_vline(xintercept = map_estimate(posteriorsaa$HCT_Accuracy), color = "purple", linewidth = 1)

range(posteriorsaa$HCT_Accuracy)

hdi(posteriorsaa$HCT_Accuracy, ci = 0.89)

describe_posterior(modelaa, test = c("p_direction", "rope", "bayesfactor"))

resultaa <- correlationBF(clean$PI_Alive, clean$HCT_Accuracy)
describe_posterior(resultaa)
```

#### Posterior for PI-hierarchical and HCT-accuracy (result not ideal)
```{r}
modelha <- stan_glm(PI_Hierarchical ~ HCT_Accuracy, data = clean)

posteriorsha <- get_parameters(modelha)

head(posteriorsha)

ggplot(posteriorsha, aes(x = HCT_Accuracy)) +
  geom_density(fill = "orange")

mean(posteriorsha$HCT_Accuracy)

median(posteriorsha$HCT_Accuracy)

map_estimate(posteriorsha$HCT_Accuracy)

ggplot(posteriorsha, aes(x = HCT_Accuracy)) +
  geom_density(fill = "orange") +
  # The mean in blue
  geom_vline(xintercept = mean(posteriorsha$HCT_Accuracy), color = "blue", linewidth = 1) +
  # The median in red
  geom_vline(xintercept = median(posteriorsha$HCT_Accuracy), color = "red", linewidth = 1) +
  # The MAP in purple
  geom_vline(xintercept = map_estimate(posteriorsha$HCT_Accuracy), color = "purple", linewidth = 1)

range(posteriorsha$HCT_Accuracy)

hdi(posteriorsha$HCT_Accuracy, ci = 0.89)

describe_posterior(modelha, test = c("p_direction", "rope", "bayesfactor"))

resultha <- correlationBF(clean$PI_Hierarchical, clean$HCT_Accuracy)
describe_posterior(resultha)
```

#### Posterior for PI-understandable and HCT-accuracy (result not ideal)

```{r}
modelua <- stan_glm(PI_Understandable ~ HCT_Accuracy, data = clean)

posteriorsua <- get_parameters(modelua)

head(posteriorsua)

ggplot(posteriorsua, aes(x = HCT_Accuracy)) +
  geom_density(fill = "orange")

mean(posteriorsua$HCT_Accuracy)

median(posteriorsua$HCT_Accuracy)

map_estimate(posteriorsua$HCT_Accuracy)

ggplot(posteriorsua, aes(x = HCT_Accuracy)) +
  geom_density(fill = "orange") +
  # The mean in blue
  geom_vline(xintercept = mean(posteriorsua$HCT_Accuracy), color = "blue", linewidth = 1) +
  # The median in red
  geom_vline(xintercept = median(posteriorsua$HCT_Accuracy), color = "red", linewidth = 1) +
  # The MAP in purple
  geom_vline(xintercept = map_estimate(posteriorsua$HCT_Accuracy), color = "purple", linewidth = 1)

range(posteriorsua$HCT_Accuracy)

hdi(posteriorsua$HCT_Accuracy, ci = 0.89)

describe_posterior(modelha, test = c("p_direction", "rope", "bayesfactor"))

resultha <- correlationBF(clean$PI_Understandable, clean$HCT_Accuracy)
describe_posterior(resultha)
```

### Correlation tests
#### IAS and HCT
```{r}
ih <- dplyr::select(clean, IAS_TOTAL, HCT_Accuracy, HCT_Awareness, HCT_Sensibility)
ihplot <- correlation(ih)
ihplot %>%
  summary(redundant = TRUE) %>%
  plot()
```

#### MAIA and HCT
```{r}
mh <- dplyr::select(clean, MAIA_Noticing, HCT_Accuracy, HCT_Awareness, HCT_Sensibility)
mhplot <- correlation(mh)
mhplot %>%
  summary(redundant = TRUE) %>%
  plot()
```

#### MAIA and IAS
```{r}
mi <- dplyr::select(clean, MAIA_Noticing, IAS_TOTAL)
miplot <- correlation(mi)
miplot %>%
  summary(redundant = TRUE) %>%
  plot()
```

#### MAIA and IAS and HCT
```{r}
mih <- dplyr::select(clean, MAIA_Noticing, IAS_TOTAL, HCT_Accuracy, HCT_Awareness, HCT_Sensibility)
mihplot <- correlation(mih)
mihplot %>%
  summary(redundant = TRUE) %>%
  plot()

cormih <- cor(mih)
corrplot(cormih, method = "square", order = "FPC", type = "lower", diag = FALSE)
```
#### IAS and PI
```{r}
ip <- dplyr::select(clean, IAS_TOTAL, PI_Alive, PI_Understandable, PI_Hierarchical)
ipplot <- correlation(ip)
ipplot %>%
  summary(redundant = TRUE) %>%
  plot()
```

#### MAIA and PI
```{r}
mp <- dplyr::select(clean, MAIA_Noticing, PI_Alive, PI_Understandable, PI_Hierarchical)
mpplot <- correlation(mp)
mpplot %>%
  summary(redundant = TRUE) %>%
  plot()
```

#### HCT and PI
```{r}
hp <- dplyr::select(clean, HCT_Accuracy, HCT_Awareness, HCT_Sensibility, PI_Alive, PI_Understandable, PI_Hierarchical)
hpplot <- correlation(hp)
hpplot %>%
  summary(redundant = TRUE) %>%
  plot()

corhp <- cor(hp)
corrplot(corhp, method = "square", order = "FPC", type = "lower", diag = FALSE)
```

#### Posterior for MAIA-noticing and HCT-awareness (since they both involves awareness of internal signals) (result not ideal)
```{r}
modelnoaw <- stan_glm(MAIA_Noticing ~ HCT_Awareness, data = clean)

posteriorsnoaw <- get_parameters(modelnoaw)

head(posteriorsnoaw)

ggplot(posteriorsnoaw, aes(x = HCT_Awareness)) +
  geom_density(fill = "orange")

mean(posteriorsnoaw$HCT_Awareness)

median(posteriorsnoaw$HCT_Awareness)

map_estimate(posteriorsnoaw$HCT_Awareness)

ggplot(posteriorsnoaw, aes(x = HCT_Awareness)) +
  geom_density(fill = "orange") +
  # The mean in blue
  geom_vline(xintercept = mean(posteriorsnoaw$HCT_Awareness), color = "blue", linewidth = 1) +
  # The median in red
  geom_vline(xintercept = median(posteriorsnoaw$HCT_Awareness), color = "red", linewidth = 1) +
  # The MAP in purple
  geom_vline(xintercept = map_estimate(posteriorsnoaw$HCT_Awareness), color = "purple", linewidth = 1)

range(posteriorsnoaw$HCT_Awareness)

hdi(posteriorsnoaw$HCT_Awareness, ci = 0.89)

describe_posterior(modelnoaw, test = c("p_direction", "rope", "bayesfactor"))

resultnoaw <- correlationBF(clean$MAIA_Noticing, clean$HCT_Awareness)
describe_posterior(resultnoaw)
```

