---
title: "Preprocessing"
format: html
editor:
    render-on-save: true
execute:
  cache: true
---

## Descriptive Statistics
```{r}
#| output: false
library(tidyverse)
library(easystats)
library(rstanarm)
library(bayestestR)
library(insight)
library(see)
library(corrplot)

df <- read.csv("./data/data.csv")
```
### Participants
```{r}
report_participants(df, age = "Age", gender = "Gender", race = "Ethnicity")
```

### Tidy up raw data
```{r}
df <- df |>
    mutate(IAS_TOTAL = (IAS_1 + IAS_2 + IAS_3 + IAS_4 + IAS_5 + IAS_6 + IAS_7 + IAS_8 + IAS_9 + IAS_10 + IAS_11 + IAS_12 + IAS_13 + IAS_14 +        IAS_15 + IAS_16 + IAS_17 + IAS_18 + IAS_19 + IAS_20 + IAS_21)/21)

df <- df |>
    mutate(MAIA_NOTIC = (MAIA_Noticing_1 + MAIA_Noticing_2 + MAIA_Noticing_3 + MAIA_Noticing_4)/4)
```

### Selecting relevant variables
```{r}
clean <- df |>
    select(participant_id, IAS_TOTAL, MAIA_NOTIC, PI_Alive, PI_Understandable, PI_Hierarchical, HCT_Accuracy, HCT_Awareness, HCT_Sensibility)
```

### Safe cleaned data
```{r}
write.csv(clean, "./data/data_clean.csv")
```

### Bayes
#### Posterior for PI-alive and HCT-accuracy
```{r}
modelaa <- stan_glm(PI_Alive ~ HCT_Accuracy, data = clean)

posteriorsaa <- get_parameters(modelaa)

head(posteriorsaa)

ggplot(posteriorsaa, aes(x = HCT_Accuracy)) +
  geom_density(fill = "orange")

mean(posteriorsaa$HCT_Accuracy)

median(posteriorsaa$HCT_Accuracy)

map_estimate(posteriorsaa$HCT_Accuracy)

ggplot(posteriorsaa, aes(x = HCT_Accuracy)) +
  geom_density(fill = "orange") +
  # The mean in blue
  geom_vline(xintercept = mean(posteriorsaa$HCT_Accuracy), color = "blue", linewidth = 1) +
  # The median in red
  geom_vline(xintercept = median(posteriorsaa$HCT_Accuracy), color = "red", linewidth = 1) +
  # The MAP in purple
  geom_vline(xintercept = map_estimate(posteriorsaa$HCT_Accuracy), color = "purple", linewidth = 1)

range(posteriorsaa$HCT_Accuracy)

hdi(posteriorsaa$HCT_Accuracy, ci = 0.89)

describe_posterior(modelaa, test = c("p_direction", "rope", "bayesfactor"))

resultaa <- correlationBF(clean$PI_Alive, clean$HCT_Accuracy)
describe_posterior(resultaa)
```
#### Posterior for PI-hierarchical and HCT-accuracy (result not ideal)
```{r}
modelha <- stan_glm(PI_Hierarchical ~ HCT_Accuracy, data = clean)

posteriorsha <- get_parameters(modelha)

head(posteriorsha)

ggplot(posteriorsha, aes(x = HCT_Accuracy)) +
  geom_density(fill = "orange")

mean(posteriorsha$HCT_Accuracy)

median(posteriorsha$HCT_Accuracy)

map_estimate(posteriorsha$HCT_Accuracy)

ggplot(posteriorsha, aes(x = HCT_Accuracy)) +
  geom_density(fill = "orange") +
  # The mean in blue
  geom_vline(xintercept = mean(posteriorsha$HCT_Accuracy), color = "blue", linewidth = 1) +
  # The median in red
  geom_vline(xintercept = median(posteriorsha$HCT_Accuracy), color = "red", linewidth = 1) +
  # The MAP in purple
  geom_vline(xintercept = map_estimate(posteriorsha$HCT_Accuracy), color = "purple", linewidth = 1)

range(posteriorsha$HCT_Accuracy)

hdi(posteriorsha$HCT_Accuracy, ci = 0.89)

describe_posterior(modelha, test = c("p_direction", "rope", "bayesfactor"))

resultha <- correlationBF(clean$PI_Hierarchical, clean$HCT_Accuracy)
describe_posterior(resultha)
```

#### Posterior for PI-understandable and HCT-accuracy (result not ideal)
```{r}
modelua <- stan_glm(PI_Understandable ~ HCT_Accuracy, data = clean)

posteriorsua <- get_parameters(modelua)

head(posteriorsua)

ggplot(posteriorsua, aes(x = HCT_Accuracy)) +
  geom_density(fill = "orange")

mean(posteriorsua$HCT_Accuracy)

median(posteriorsua$HCT_Accuracy)

map_estimate(posteriorsua$HCT_Accuracy)

ggplot(posteriorsua, aes(x = HCT_Accuracy)) +
  geom_density(fill = "orange") +
  # The mean in blue
  geom_vline(xintercept = mean(posteriorsua$HCT_Accuracy), color = "blue", linewidth = 1) +
  # The median in red
  geom_vline(xintercept = median(posteriorsua$HCT_Accuracy), color = "red", linewidth = 1) +
  # The MAP in purple
  geom_vline(xintercept = map_estimate(posteriorsua$HCT_Accuracy), color = "purple", linewidth = 1)

range(posteriorsua$HCT_Accuracy)

hdi(posteriorsua$HCT_Accuracy, ci = 0.89)

describe_posterior(modelha, test = c("p_direction", "rope", "bayesfactor"))

resultha <- correlationBF(clean$PI_Understandable, clean$HCT_Accuracy)
describe_posterior(resultha)
```

### Correlation tests
#### IAS and HCT
```{r}
ih <- dplyr::select(clean, IAS_TOTAL, HCT_Accuracy, HCT_Awareness, HCT_Sensibility)
ihplot <- correlation(ih)
ihplot %>%
  summary(redundant = TRUE) %>%
  plot()
```

#### MAIA and HCT
```{r}
mh <- dplyr::select(clean, MAIA_NOTIC, HCT_Accuracy, HCT_Awareness, HCT_Sensibility)
mhplot <- correlation(mh)
mhplot %>%
  summary(redundant = TRUE) %>%
  plot()
```

#### MAIA and IAS
```{r}
mi <- dplyr::select(clean, MAIA_NOTIC, IAS_TOTAL)
miplot <- correlation(mi)
miplot %>%
  summary(redundant = TRUE) %>%
  plot()
```

#### MAIA and IAS and HCT
```{r}
mih <- dplyr::select(clean, MAIA_NOTIC, IAS_TOTAL, HCT_Accuracy, HCT_Awareness, HCT_Sensibility)
mihplot <- correlation(mih)
mihplot %>%
  summary(redundant = TRUE) %>%
  plot()

cormih = cor(mih)
corrplot(cormih, method = 'square', order = 'FPC', type = 'lower', diag = FALSE)
```
#### IAS and PI
```{r}
ip <- dplyr::select(clean, IAS_TOTAL, PI_Alive, PI_Understandable, PI_Hierarchical)
ipplot <- correlation(ip)
ipplot %>%
  summary(redundant = TRUE) %>%
  plot()
```

#### MAIA and PI
```{r}
mp <- dplyr::select(clean, MAIA_NOTIC, PI_Alive, PI_Understandable, PI_Hierarchical)
mpplot <- correlation(mp)
mpplot %>%
  summary(redundant = TRUE) %>%
  plot()
```

#### HCT and PI
```{r}
hp <- dplyr::select(clean, HCT_Accuracy, HCT_Awareness, HCT_Sensibility, PI_Alive, PI_Understandable, PI_Hierarchical)
hpplot <- correlation(hp)
hpplot %>%
  summary(redundant = TRUE) %>%
  plot()

corhp = cor(hp)
corrplot(corhp, method = 'square', order = 'FPC', type = 'lower', diag = FALSE)
```

#### Posterior for MAIA-noticing and HCT-awareness (since they both involves awareness of internal signals) (result not ideal)
```{r}
modelnoaw <- stan_glm(MAIA_NOTIC ~ HCT_Awareness, data = clean)

posteriorsnoaw <- get_parameters(modelnoaw)

head(posteriorsnoaw)

ggplot(posteriorsnoaw, aes(x = HCT_Awareness)) +
  geom_density(fill = "orange")

mean(posteriorsnoaw$HCT_Awareness)

median(posteriorsnoaw$HCT_Awareness)

map_estimate(posteriorsnoaw$HCT_Awareness)

ggplot(posteriorsnoaw, aes(x = HCT_Awareness)) +
  geom_density(fill = "orange") +
  # The mean in blue
  geom_vline(xintercept = mean(posteriorsnoaw$HCT_Awareness), color = "blue", linewidth = 1) +
  # The median in red
  geom_vline(xintercept = median(posteriorsnoaw$HCT_Awareness), color = "red", linewidth = 1) +
  # The MAP in purple
  geom_vline(xintercept = map_estimate(posteriorsnoaw$HCT_Awareness), color = "purple", linewidth = 1)

range(posteriorsnoaw$HCT_Awareness)

hdi(posteriorsnoaw$HCT_Awareness, ci = 0.89)

describe_posterior(modelnoaw, test = c("p_direction", "rope", "bayesfactor"))

resultnoaw <- correlationBF(clean$MAIA_NOTIC, clean$HCT_Awareness)
describe_posterior(resultnoaw)
```

